Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-04-28 Manuscript/PLoSONESubmission/OnlineAppendices-LaTeXSuppFiles/SupportingInformation3.tex

@@

%Summary of the BC between pairs of methods for the ML parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised distance between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds distance (RF) or the Normalised Triplets distance (Tr).}
\label{Tab_Supp_summary_BC_ML}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ 
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.30 & 0.31 & 0.69 & 0.61 & 0.77 & 1.00 \\ 
                                                                       & $Tr$ & 0.79 & 0.81 & 0.84 & 0.86 & 0.85 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.22 & 0.29 & 0.36 & 0.54 & 0.69 \\ 
                                                                       & $Tr$ & 0.08 & 0.42 & 0.53 & 0.51 & 0.74 & 0.78 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.49 & 0.61 & 0.51 & 0.67 & 0.74 \\ 
                                                                       & $Tr$ & 0.21 & 0.61 & 0.70 & 0.63 & 0.81 & 0.81 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.01 & 0.02 & 0.02 & 0.02 & 0.03 & 0.04 \\ 
                                                                       & $Tr$ & 0.08 & 0.69 & 0.78 & 0.64 & 0.79 & 0.84 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.01 & 0.02 & 0.02 & 0.04 & 0.08 & 0.09 \\ 
                                                                       & $Tr$ & 0.21 & 0.74 & 0.75 & 0.68 & 0.84 & 0.87 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.75 & 0.85 & 0.85 & 0.95 & 1.00 \\ 
                                                                       & $Tr$ & 0.91 & 0.92 & 0.96 & 0.95 & 0.97 & 0.98 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

%Summary of the BC between pairs of methods for the MF parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised distance between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds distance (RF) or the Normalised Triplets distance (Tr).}
\label{Tab_Supp_summary_BC_MF}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\  
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.00 & 0.25 & 0.48 & 0.50 & 0.76 & 1.00 \\ 
                                                                       & $Tr$ & 0.38 & 0.69 & 0.75 & 0.72 & 0.80 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.18 & 0.32 & 0.36 & 0.47 & 0.77 \\ 
                                                                       & $Tr$ & 0.08 & 0.34 & 0.40 & 0.38 & 0.53 & 0.55 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.47 & 0.71 & 0.60 & 0.86 & 0.94 \\ 
                                                                       & $Tr$ & 0.21 & 0.54 & 0.62 & 0.56 & 0.64 & 0.80 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.00 & 0.00 & 0.01 & 0.01 & 0.01 & 0.03 \\ 
                                                                       & $Tr$ & 0.08 & 0.38 & 0.54 & 0.49 & 0.70 & 0.75 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.00 & 0.02 & 0.02 & 0.02 & 0.04 & 0.04 \\ 
                                                                       & $Tr$ & 0.21 & 0.29 & 0.66 & 0.54 & 0.72 & 0.82 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.69 & 0.72 & 0.71 & 0.72 & 0.72 \\ 
                                                                       & $Tr$ & 0.91 & 0.91 & 0.91 & 0.93 & 0.92 & 0.98 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

%Summary of the BC between pairs of methods for the MC parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised distance between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds distance (RF) or the Normalised Triplets distance (Tr).}
\label{Tab_Supp_summary_BC_MC}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\  
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.03 & 0.32 & 0.66 & 0.55 & 0.75 & 1.00 \\ 
                                                                       & $Tr$ & 0.51 & 0.69 & 0.80 & 0.76 & 0.80 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.17 & 0.21 & 0.31 & 0.46 & 0.68 \\ 
                                                                       & $Tr$ & 0.08 & 0.31 & 0.39 & 0.39 & 0.56 & 0.61 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.44 & 0.47 & 0.52 & 0.78 & 0.90 \\ 
                                                                       & $Tr$ & 0.21 & 0.52 & 0.59 & 0.55 & 0.66 & 0.77 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.00 & 0.01 & 0.01 & 0.02 & 0.02 & 0.03 \\ 
                                                                       & $Tr$ & 0.08 & 0.47 & 0.62 & 0.51 & 0.66 & 0.73 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.00 & 0.02 & 0.04 & 0.04 & 0.05 & 0.06 \\ 
                                                                       & $Tr$ & 0.21 & 0.45 & 0.64 & 0.57 & 0.74 & 0.79 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.73 & 0.73 & 0.76 & 0.81 & 0.86 \\ 
                                                                       & $Tr$ & 0.91 & 0.92 & 0.93 & 0.94 & 0.96 & 0.99 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

>>>>

\documentclass[12pt,letterpaper]{article}

%Packages
\usepackage{pdflscape}
\usepackage{fixltx2e}
\usepackage{textcomp}
\usepackage{fullpage}
\usepackage{float}
\usepackage{latexsym}
\usepackage{url}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{bm}
\usepackage{array}
\usepackage[version=3]{mhchem}
\usepackage{ifthen}
\usepackage{caption}
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{amstext}
\usepackage{enumerate}
\usepackage[osf]{mathpazo}
\usepackage{dcolumn}
\usepackage{lineno}
\pagenumbering{arabic}

%Pagination style and stuff
\linespread{2}
\raggedright
\setlength{\parindent}{0.5in}
\setcounter{secnumdepth}{0} 
\renewcommand{\section}[1]{%
\bigskip
\begin{center}
\begin{Large}
\normalfont\scshape #1
\medskip
\end{Large}
\end{center}}
\renewcommand{\subsection}[1]{%
\bigskip
\begin{center}
\begin{large}
\normalfont\itshape #1
\end{large}
\end{center}}
\renewcommand{\subsubsection}[1]{%
\vspace{2ex}
\noindent
\textit{#1.}---}
\renewcommand{\tableofcontents}{}

\begin{document}

\section{Supporting Information S3: Additional Results}

@@

%Summary of the BC between pairs of methods for the ML parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised distance between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds distance (RF) or the Normalised Triplets distance (Tr) for the $M_{L}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_ML}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\ 
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.30 & 0.31 & 0.69 & 0.61 & 0.77 & 1.00 \\ 
                                                                       & $Tr$ & 0.79 & 0.81 & 0.84 & 0.86 & 0.85 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.22 & 0.29 & 0.36 & 0.54 & 0.69 \\ 
                                                                       & $Tr$ & 0.08 & 0.42 & 0.53 & 0.51 & 0.74 & 0.78 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.49 & 0.61 & 0.51 & 0.67 & 0.74 \\ 
                                                                       & $Tr$ & 0.21 & 0.61 & 0.70 & 0.63 & 0.81 & 0.81 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.01 & 0.02 & 0.02 & 0.02 & 0.03 & 0.04 \\ 
                                                                       & $Tr$ & 0.08 & 0.69 & 0.78 & 0.64 & 0.79 & 0.84 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.01 & 0.02 & 0.02 & 0.04 & 0.08 & 0.09 \\ 
                                                                       & $Tr$ & 0.21 & 0.74 & 0.75 & 0.68 & 0.84 & 0.87 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.75 & 0.85 & 0.85 & 0.95 & 1.00 \\ 
                                                                       & $Tr$ & 0.91 & 0.92 & 0.96 & 0.95 & 0.97 & 0.98 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

%Summary of the BC between pairs of methods for the MF parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised distance between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds distance (RF) or the Normalised Triplets distance (Tr) for the $M_{F}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_MF}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\  
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.00 & 0.25 & 0.48 & 0.50 & 0.76 & 1.00 \\ 
                                                                       & $Tr$ & 0.38 & 0.69 & 0.75 & 0.72 & 0.80 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.18 & 0.32 & 0.36 & 0.47 & 0.77 \\ 
                                                                       & $Tr$ & 0.08 & 0.34 & 0.40 & 0.38 & 0.53 & 0.55 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.47 & 0.71 & 0.60 & 0.86 & 0.94 \\ 
                                                                       & $Tr$ & 0.21 & 0.54 & 0.62 & 0.56 & 0.64 & 0.80 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.00 & 0.00 & 0.01 & 0.01 & 0.01 & 0.03 \\ 
                                                                       & $Tr$ & 0.08 & 0.38 & 0.54 & 0.49 & 0.70 & 0.75 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.00 & 0.02 & 0.02 & 0.02 & 0.04 & 0.04 \\ 
                                                                       & $Tr$ & 0.21 & 0.29 & 0.66 & 0.54 & 0.72 & 0.82 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.69 & 0.72 & 0.71 & 0.72 & 0.72 \\ 
                                                                       & $Tr$ & 0.91 & 0.91 & 0.91 & 0.93 & 0.92 & 0.98 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}

%Summary of the BC between pairs of methods for the MC parameter
\begin{landscape}
\begin{table}[ht]
\caption{Bhattacharyya Coefficients of the pairwise method comparisons, each of which corresponds to the normalised distance between the "best" tree and the "missing data" using either the Normalised Robinson-Foulds distance (RF) or the Normalised Triplets distance (Tr) for the $M_{C}$ missing data parameter only.}
\label{Tab_Supp_summary_BC_MC}
\centering
\begin{tabular}{lccccccc}
  \hline
 Comparison &  Metric & Min. & 1st Qu. & Median & Mean & 3rd Qu. & Max. \\  
  \hline
    Maximum Likelihood \textit{vs.} Bayesian consensus                 & $RF$ & 0.03 & 0.32 & 0.66 & 0.55 & 0.75 & 1.00 \\ 
                                                                       & $Tr$ & 0.51 & 0.69 & 0.80 & 0.76 & 0.80 & 1.00 \\ 
    Maximum Likelihood \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.03 & 0.17 & 0.21 & 0.31 & 0.46 & 0.68 \\ 
                                                                       & $Tr$ & 0.08 & 0.31 & 0.39 & 0.39 & 0.56 & 0.61 \\ 
    Maximum Likelihood \textit{vs.} Bayesian posterior trees           & $RF$ & 0.02 & 0.44 & 0.47 & 0.52 & 0.78 & 0.90 \\ 
                                                                       & $Tr$ & 0.21 & 0.52 & 0.59 & 0.55 & 0.66 & 0.77 \\ 
    Bayesian consensus \textit{vs.} Maximum Likelihood bootstraps      & $RF$ & 0.00 & 0.01 & 0.01 & 0.02 & 0.02 & 0.03 \\ 
                                                                       & $Tr$ & 0.08 & 0.47 & 0.62 & 0.51 & 0.66 & 0.73 \\ 
    Bayesian consensus \textit{vs.} Bayesian posterior trees           & $RF$ & 0.00 & 0.02 & 0.04 & 0.04 & 0.05 & 0.06 \\ 
                                                                       & $Tr$ & 0.21 & 0.45 & 0.64 & 0.57 & 0.74 & 0.79 \\ 
    Bayesian posterior tree \textit{vs.} Maximum Likelihood bootstraps & $RF$ & 0.69 & 0.73 & 0.73 & 0.76 & 0.81 & 0.86 \\ 
                                                                       & $Tr$ & 0.91 & 0.92 & 0.93 & 0.94 & 0.96 & 0.99 \\ 
   \hline
\end{tabular}
\end{table}
\end{landscape}
%END
\end{document}
